Local PCA results

### 2016-05-07 medicago/medicago_data_setup.Rmd
.

```{r setup}
devtools::load_all("../package")
library(Matrix)
library(colorspace)
```

@@

>>>>

```{r setup}
devtools::load_all("../package")
library(Matrix)
library(colorspace)
options(width=100)
```

@@

So, thats a SNP every 10bp.
Since we have `r length(bcf.samples)` samples,
each local PC will take `r 1+length(bcf.samples)` doubles to record;
a double is 8 bytes;
so in, say 1Gb we can fit one local PC for `r floor(1e9 / (8*(1+length(bcf.samples))))` windows.
With a total of `r sum(chrom.stats['nsnps',])` SNPs,
that'd be `r floor(sum(chrom.stats['nsnps',])/floor(1e9 / (8*(1+length(bcf.samples)))))` SNPs per window.
A bigger concern is the distance matrix we compute between windows
(we don't have to save this to disk, though).
With this many windows, that would be `r floor(1e9 / (8*(1+length(bcf.samples))))^2` floats,
or `r floor(1e9 / (8*(1+length(bcf.samples))))^2 / 8e9` Gb.
That's still possible, but barely.
